Untitled

### 2021-06-11 data-raw/Download.Rmd
updated instructions

Check out this as an example: https://github.com/rudeboybert/fivethirtyeight/blob/master/data-raw/process_data_sets.R

>>>>

Check out thes as an example:

* https://github.com/rudeboybert/fivethirtyeight/blob/master/data-raw/process_data_sets.R to load data into package
* https://github.com/rudeboybert/fivethirtyeight/blob/master/R/data.R#L22 to write help file using `roxygen2`
